\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{titlesec}

\titleformat{\section}{\Large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\Huge Snapshot Objectives}\\[0.5cm]
    {\Large Travel Request Web Application}\\[0.25cm]
    {\large Version 1.0 -- \today}
\end{center}

\vspace{1cm}

\section{Snapshot 1: Basic Skeleton and Core Flow}

\begin{itemize}
    \item Set up Flask project structure (\texttt{src/}, \texttt{templates/}, \texttt{requirements.txt}).
    \item Implement basic routes:
    \begin{itemize}
        \item \texttt{/login}
        \item \texttt{/dashboard}
    \end{itemize}
    \item Create simple HTML templates for login and dashboard.
    \item Add SQLite database configuration and define:
    \begin{itemize}
        \item \texttt{User} model
        \item \texttt{TravelRequest} model (initial fields)
    \end{itemize}
    \item Seed demo users (employee and manager).
    \item Verify that a user can log in and see a basic dashboard.
\end{itemize}

\section{Snapshot 2: Travel Request Creation and History}

\begin{itemize}
    \item Implement \texttt{/requests/new} route and template.
    \item Add form validation for destination, dates, cost, and reason.
    \item Save new requests in the database with status \texttt{Pending}.
    \item Implement \texttt{/requests/my} to show:
    \begin{itemize}
        \item All requests for the logged-in user.
        \item Destination, dates, cost, submitted date, status.
    \end{itemize}
    \item Add basic filtering or tabs (All, Pending, Approved) if time allows.
    \item Create initial TestRail test cases for:
    \begin{itemize}
        \item Login.
        \item New request submission.
        \item Viewing request history.
    \end{itemize}
\end{itemize}

\section{Snapshot 3: Manager Portal and Decision Flow}

\begin{itemize}
    \item Implement \texttt{/requests/manage} route and manager-only access.
    \item Show all requests with:
    \begin{itemize}
        \item Employee name
        \item Destination
        \item Estimated cost
        \item Status
    \end{itemize}
    \item Implement request detail page \texttt{/requests/<id>}:
    \begin{itemize}
        \item Display full request information.
        \item Manager actions: Approve, Deny, Mark Settled.
        \item Store manager comment.
    \end{itemize}
    \item Update history and manager views so status changes are visible.
    \item Add more TestRail tests to cover:
    \begin{itemize}
        \item Manager approval flow.
        \item Denial with comment.
        \item Settling a request.
    \end{itemize}
\end{itemize}

\section{Snapshot 4: Polishing, Validation, and Documentation}

\begin{itemize}
    \item Improve UI with clearer alerts and labels.
    \item Add extra validation checks (for example, start date before end date).
    \item Clean up navigation (logout button, consistent header).
    \item Finalize:
    \begin{itemize}
        \item SRS Version 2.0
        \item SDD Version 2.0
        \item README / User Manual
        \item Design Specification
    \end{itemize}
    \item Run full TestRail test run and export reports for submission.
    \item Verify GitHub repository structure and prepare final submission.
\end{itemize}

\end{document}
